### 2015-05-15 whoop.tex
Cut to the chase in the abstract.
Removed subsections from background and replaced with paragraph headings.  A bit reluctant to do this, but I think it makes sense to save cutting too much text.

\noindent\textbf{Lockset Instrumentation }
%
For templates $T$ and $U$ (including the possibility that $T$ and $U$ are equal) we want to check whether it is possible for a thread executing $T$ to race with a thread executing $U$, in the presence of arbitrarily many further concurrently executing threads.
%
To this end, we first \emph{instrument} a template $T$ for lockset analysis (see \S\ref{bg:lockset}).  Given an arbitrary symbol $i$, we define the instrumentation of $T$ with respect to $i$, denoted $\instrument{T}{i}$.  There are two aspects to this instrumentation phase: \emph{renaming} and \emph{lockset instrumentation}.

@@

\begin{figure}
\footnotesize
\begin{tabular}{l}
$\currentlockset{i} = \emptyset;$ $\hasbeenread{i} = \emptyset;$ $\hasbeenwritten{i} = \emptyset;$ \\
$\currentlockset{j} = \emptyset;$ $\hasbeenread{j} = \emptyset;$ $\hasbeenwritten{j} = \emptyset;$ \\
\texttt{for} $s \in \sharedvars$ \texttt{do} $\lockset{s}{i} = \mutexes;$ $\lockset{s}{j} = \mutexes;$ \medskip
\\

$\mainforthread{\instrument{T}{i}}();$ \\
$\mainforthread{\instrument{U}{j}}();$ \medskip\\

@@

\end{tabular}
\caption{The sequential program to be analyzed in order to prove race-freedom for a pair of thread templates}
\label{fig:sequentialization}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=.99\linewidth]{img/whoop.pdf}
\caption{The \whoop architecture, empowered by state-of-the-art compilation (Clang/LLVM and SMACK) and verification (Boogie and \corral) tools}
\label{fig:whoop}
\end{figure*}

@@

\begin{figure}[t]
\begin{lstlisting}
const struct file_operations nvram_fops = {
  .llseek = nvram_llseek,
  .read = read_nvram,
  .write = write_nvram,
  .unlocked_ioctl = nvram_unlocked_ioctl
};
\end{lstlisting}
\caption{Entry points definitions in the generic\_nvram driver}
\label{fig:entrypoints}
\end{figure}

@@

\begin{lstlisting}[keywordstyle=\ttfamily]
generic_nvram.c: error: potential read-write race:
  read by entry point nvram_llseek, generic_nvram.c:54:2
    return file->f_pos;
  write by entry point nvram_llseek, generic_nvram.c:53:2
    file->f_pos = offset;
\end{lstlisting}

>>>>

\noindent\textbf{Lockset Instrumentation }
%
For templates $T$ and $U$ (including the possibility that $T$ and $U$ are equal) we want to check whether it is possible for a thread executing $T$ to race with a thread executing $U$, in the presence of arbitrarily many further concurrently executing threads.
%
To this end, we first \emph{instrument} a template $T$ for lockset analysis (see \S\ref{sec:background}).  Given an arbitrary symbol $i$, we define the instrumentation of $T$ with respect to $i$, denoted $\instrument{T}{i}$.  There are two aspects to this instrumentation phase: \emph{renaming} and \emph{lockset instrumentation}.

@@

\begin{figure}
\footnotesize
\begin{tabular}{l}
$\currentlockset{i} = \emptyset;$ $\hasbeenread{i} = \emptyset;$ $\hasbeenwritten{i} = \emptyset;$ \\
$\currentlockset{j} = \emptyset;$ $\hasbeenread{j} = \emptyset;$ $\hasbeenwritten{j} = \emptyset;$ \\
\texttt{for} $s \in \sharedvars$ \texttt{do} $\lockset{s}{i} = \mutexes;$ $\lockset{s}{j} = \mutexes;$ \smallskip
\\

$\mainforthread{\instrument{T}{i}}();$ \\
$\mainforthread{\instrument{U}{j}}();$ \smallskip\\

@@

\end{tabular}
\caption{The sequential program to be analyzed in order to prove race-freedom for a pair of thread templates}
\label{fig:sequentialization}
\vspace{-2mm}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=.99\linewidth]{img/whoop.pdf}
\vspace{-2mm}
\caption{The \whoop architecture, empowered by state-of-the-art compilation (Clang/LLVM and SMACK) and verification (Boogie and \corral) tools}
\vspace{-2mm}
\label{fig:whoop}
\end{figure*}

@@

\begin{figure}[t]
\begin{lstlisting}
const struct file_operations nvram_fops = {
  .llseek = nvram_llseek,
  .read = read_nvram,
  .write = write_nvram,
  .unlocked_ioctl = nvram_unlocked_ioctl
};
\end{lstlisting}
\vspace{-2mm}
\caption{Entry point definitions in the generic\_nvram driver}
\label{fig:entrypoints}
\vspace{-2mm}
\end{figure}

@@

\begin{lstlisting}[keywordstyle=\ttfamily]
generic_nvram.c: error: potential read-write race:
  read by entry point nvram_llseek, generic_nvram.c:54:2
    return file->f_pos;
  write by entry point nvram_llseek, generic_nvram.c:53:2
    file->f_pos = offset;
\end{lstlisting}
\vspace{-2mm}
